---
format: html
editor: visual
execute:
  eval: false
---

[Hands-on sessions](index.html) / [Hands-on session 2](exercise_session_2.html) /

## Upload and chat about a document

One use case of LLMs that has become popular is providing a document (for example, a PDF file) and chatting with LLMs about the content. For example, you can ask it to summarize, answer specific questions, find weaknesses and strengths, rewrite sections, and so on.

In order to test this out you can use your own document or download one of our suggestions:

-   <a href="https://www.scilifelab.se/wp-content/uploads/2020/05/scilifelab-roadmap-2020-2030_final.pdf">SciLifeLab Roadmap for 2020-2030</a>;
-   <a href="https://www.scilifelab.se/wp-content/uploads/2024/02/SciLifeLab-arsrapport-2023.pdf">SciLifeLab annual report 2023</a>;
-   [Antibiotic perseverance increases the risk of resistance development (Brandis, Larsson, Elf, *PNAS 2023*)](https://www.pnas.org/doi/pdf/10.1073/pnas.2216216120?download=true).

> ☝️ **TIP**: You can upload a document in Swedish but ask questions in English and vice versa because the LLM can just translate between them.

### Microsoft Copilot

If you have access to Microsoft Copilot via your university then you can simply use the upload function in the chat to upload a PDF file and then ask it to answer questions.

```{r}
I am uploading a PDF file. Summarize the content.
```

> ☝️ **TIP**: If you run into a file size limitation, try the free alternative that we suggest below.

### Free alternatives

There is a number of free alternatives that you can find online. One of those is <a href="https://www.chatpdf.com/">https://www.chatpdf.com/</a>. You simply upload your PDF document here and start asking questions. One nice feature of this tool is that it tells you where it found the answer to your question. For example, I uploaded the SciLifeLab annual report 2023 and asked the following.

```{r}
What was the total budget of SciLifeLab in 2023?
```
