---
format: html
editor: visual
execute:
  eval: false
---

[Hands-on sessions](index.html) / [Hands-on session 2](exercise_session_2.html) /

## Upload and chat about a document

One use case of LLMs that has become popular is providing a document (for example, a PDF file) and chatting with LLMs about the content. An alternative that will work with some of the LLM tools is providing a link to the document instead of uploading it.

##### Document upload

If you have access to Microsoft Copilot via your university then you can simply use the upload function in the chat to upload a PDF file and then ask it to answer questions.

There is a number of free alternatives that you can find online. One of those is <a href="https://www.chatpdf.com/">https://www.chatpdf.com/</a>. You simply upload your PDF document here and start asking questions. One nice feature of this tool is that it tells you where it found the answer to your question.

> ☝️ **TIP**: You can upload a document in Swedish but ask questions in English and vice versa because the LLM can just translate between them.

> ☝️ **TIP**: If you run into a file size limitation on Microsoft Copilot, try the free alternative https://chatpdf.com/.

##### Example documents

In order to test this out you can use your own document or download one of our suggestions:

-   <a href="https://www.scilifelab.se/wp-content/uploads/2020/05/scilifelab-roadmap-2020-2030_final.pdf">SciLifeLab Roadmap for 2020-2030</a>;
-   <a href="https://www.scilifelab.se/wp-content/uploads/2024/02/SciLifeLab-arsrapport-2023.pdf">SciLifeLab annual report 2023</a>;
-   [Antibiotic perseverance increases the risk of resistance development (Brandis, Larsson, Elf, *PNAS 2023*)](https://www.pnas.org/doi/pdf/10.1073/pnas.2216216120?download=true).

### Asking for information from the document

For example, we can upload the SciLifeLab annual report 2023 and ask the following.

```{r}
What was the total budget of SciLifeLab in 2023?
```

```{r}
Create an executive summary
```

```{r}
Suggest improvements
```

### Reviewing a paper

One use case is to ask to use LLMs as a tool to help review your texts.

```{r}
Act as a tired, critical reviewer who looks for reasons to deduct points from a grant application. Read and criticize the following manuscript: https://www.medrxiv.org/content/10.1101/2024.03.01.24303566v1 
```

### Summarizing documents

```{r}
Summarize the article at https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1011323
```

```{r}
List three shortcomings of the paper
```

### Finding articles

In our experience these prompts work particularly well in Microsoft Copilot and Perplexity.

```{r}
Give me one reference to a scientific paper that supports the hypothesis that imatinib is useful for treating diabetes, and another reference that it is not useful for diabetes
```

```{r}
Redo but only clinical studies
```
